Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-23 article.tex
Evolution method not sure

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_tmh_mut_rate.png}
  \caption{
    TMH mutation rates for different levels of human detection in
    two pathogens.
    Each point denotes a TMH.
    The horizontal axis denotes the percentage of Homo sapiens that
    have an HLA that binds at least one polypeptide derived from the TMH.
    The vertical axis denotes the mutation rate observed in the TMH, 
    per generation.
    At the bottom-left are undetected and conserved TMHs.
    At the top-right are TMHs that are often detected with a higher mutation
    rate, as to escape detection.
    The solid lines are obtained from a best-fitting linear model.
    The dashed horizontal line denotes the average TMH mutation rate 
    per generation in humans.
    If there is no selection, the solid lines are horizontal.
    If there is selection, the solid lines go upwards when going from left to right.
    We expect selection in viruses to be stronger, thus its line will be steeper.
    \richel{
      Stub
    }
  }
  \label{fig:tmh_mut_rate}
\end{figure}
